Modeling Ionic Polymer-Metal Composites\\ with Space-Time Adaptive Multimesh \emph{hp}-FEM

### 2010-11-03 model.tex
Results section almost re-done
Some type fixes

Hermes\footnote{http://hpfem.org/hermes} is a free and open-source C++ library 
that implements higher-order finite elements approximations and adaptive $hp$-FEM.
It supports 8 different adaptivity modes -- three isotropic and five anisotropic. 
The isotropic refinements are
\emph{h}-isotropic (H\_ISO), \emph{p}-isotropic (P\_ISO), \emph{hp}-isotropic (HP\_ISO).
Anisotropic refinement modes are
\emph{h}-anisotropic (H\_ANISO),
\emph{hp}-anisotropic-\emph{h} (HP\_ANISO\_H), \emph{p}-anisotropic (P\_ANISO),
\emph{hp}-anisotropic-p (HP\_ANISO\_P), and \emph{hp}-anisotropic (HP\_ANISO).
The eight adaptivity modes are summarized in Fig.~\ref{fig:candlist}.

\begin{figure}[!ht]
  \begin{centering}
  \includegraphics[width=0.8\columnwidth]{cand_list_quads}
  \caption{\label{fig:candlist} Refinement candidates for every
  refinement mode for quad type elements.}
  \end{centering}
\end{figure}
Note that triangular elements do not support anisotropic refinements.
Due to the large number of refinement options, classical error estimators 
that provide a constant error estimate per element, cannot be used to 
guide automatic \emph{hp}-adaptivity. 
For this, one needs to know the shape of the approximation error.
Hermes uses a pair of approximations with different orders of accuracy 
to obtain this information: coarse mesh solution and fine mesh solution. 
The initial coarse mesh is read from the mesh file, and the initial 
fine mesh is created through its global refinement both in \emph{h}
and \emph{p}. The fine mesh solution is the approximation of 
interest both during the adaptive process and at the end of computation. 
Global orthogonal projection of the fine mesh solution on the coarse mesh 
is used to extract the low-order part from the reference solution.
The adaptivity algorithm is guided by the difference between the 
reference solution and its low-order part~\cite{solin2010pde}.
Note that this approach to automatic adaptivity is PDE-independent
and thus naturally applicable to a large variety of multiphysics 
coupled problems.

>>>>

Hermes\footnote{http://hpfem.org/hermes} is a free and open-source C++ library 
that implements higher-order finite elements approximations and adaptive $hp$-FEM.
It supports 8 different adaptivity modes -- three isotropic and five anisotropic. 
The isotropic refinements are
\emph{h}-isotropic (H\_ISO), \emph{p}-isotropic (P\_ISO), \emph{hp}-isotropic (HP\_ISO).
Anisotropic refinement modes are
\emph{h}-anisotropic (H\_ANISO),
\emph{hp}-anisotropic-\emph{h} (HP\_ANISO\_H), \emph{p}-anisotropic (P\_ANISO),
\emph{hp}-anisotropic-p (HP\_ANISO\_P), and \emph{hp}-anisotropic (HP\_ANISO).
The eight adaptivity modes are summarized in Fig.~\ref{fig:candlist}. It must
be noted that in case of HP\_ANISO\_H, only element size is adapted anisotropically
whereas polynomial degree is adapted isotropically. The opposite holds true
for HP\_ANISO\_P.

\begin{figure}[!ht]
  \begin{centering}
  \includegraphics[width=0.8\columnwidth]{cand_list_quads}
  \caption{\label{fig:candlist} Refinement candidates for every
  refinement mode for quad type elements.}
  \end{centering}
\end{figure}
Note that triangular elements do not support anisotropic refinements.
Due to the large number of refinement options, classical error estimators 
that provide a constant error estimate per element, cannot be used to 
guide automatic \emph{hp}-adaptivity. 
For this, one needs to know the shape of the approximation error.
Hermes uses a pair of approximations with different orders of accuracy 
to obtain this information: coarse mesh solution and fine mesh solution~\cite{solin2010pde}. 
The initial coarse mesh is read from the mesh file, and the initial 
fine mesh is created through its global refinement both in \emph{h}
and \emph{p}. The fine mesh solution is the approximation of 
interest both during the adaptive process and at the end of computation. 
Global orthogonal projection of the fine mesh solution on the coarse mesh 
is used to extract the low-order part from the reference solution.
The adaptivity algorithm is guided by the difference between the 
reference solution and its low-order part.
Note that this approach to automatic adaptivity is PDE-independent
and thus naturally applicable to a large variety of multiphysics 
coupled problems.
